Internship Summary: Mid-Term Review

### 2020-07-20 RapportStage/Rapport.tex
add some graph

Puis on rajoute les 3 autres partitionnements \\

Puis différence entre $Y_{l0}$ et $P_l(\cos(\theta))$ (CSF). Parler de la possibilité de la base strong coupling. \\

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{RHFMiniBasRCV.pdf}
    \caption{\centering }
    \label{fig:RHFMiniBasRCV}
\end{figure}

Then we will compare the different partitioning using the same basis set. The \autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence in function of $R$ for the M{\o}ller-Plesset, the Epstein-Nesbet, the weak correlation and the strong coupling partitioning. We can see that

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{PartitioningRCV.pdf}
    \caption{\centering }
    \label{fig:RadiusPartitioning}
\end{figure}

Puis différence entre $Y_{l0}$ et $P_l(\cos(\theta))$ (CSF). + petit Parler de la possibilité de la base strong coupling avec la citation paola et les polynomes . \\
